%-------------------------
% Resume in LaTeX
%------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{color}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{fontawesome5}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

% Formatting
\urlstyle{same}
\raggedbottom
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\scshape\large\raggedright\bfseries}{}{0em}{}[\titlerule]

% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{#2} \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItem}[1]{\item \small{#1\vspace{-2pt}}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[label={-}]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Md Shafiuddin Shajib} \\ \vspace{1pt}
    Uttara, Dhaka \\ \vspace{1pt}
    \small \href{tel:+8801700651993}{\faPhone~+8801700651993} ~ 
    \href{mailto:mdshafiuddinshajib@gmail.com}{\faEnvelope~mdshafiuddinshajib@gmail.com} ~ 
    \href{https://www.linkedin.com/in/mdshafiuddinshajib/}{\faLinkedin~LinkedIn} ~
    \href{https://github.com/md-shafiuddin-shajib}{\faGithub~GitHub}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{
Motivated Computer Science graduate with foundational knowledge in web development using React.js, Node.js, and MongoDB. Experienced in building user-friendly applications and contributing to real-world projects through innovative problem-solving. A quick learner with strong teamwork, communication, and time management skills.
}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International University of Business Agriculture and Technology}{2021 -- 2024}
      {B.Sc in Computer Science and Engineering, CGPA: 3.70}{Dhaka, Bangladesh}
    \resumeSubheading
      {Adhyapak Abdul Majid College, Cumilla}{2017 -- 2019}
      {HSC, GPA: 5.00}{Cumilla, Bangladesh}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
\begin{multicols}{2}
\begin{itemize}[itemsep=0pt]
    \item Software Engineering
    \item Data Structures \& Algorithms
    \item Database Management Systems (DBMS)
    \item Web Development
    \item System Analysis and Design
    \item Object-Oriented Programming
\end{itemize}
\end{multicols}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Intern, Cyber Hundred}{May 2024 -- Aug 2024}
      {Software Developer}{Uttara, Dhaka}
      \resumeItemListStart
        \resumeItem{Developed a tour booking platform with features such as user authentication, search functionality, and review system.}
        \resumeItem{Designed responsive front-end using React.js and Redux, and integrated backend with Node.js, Express.js, and MongoDB.}
        \resumeItem{Collaborated effectively with a team of developers to ensure seamless integration of front-end and back-end components.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{#}{Tour Booking Platform} | React.js, Node.js, MongoDB}{2024}
      \resumeItemListStart
        \resumeItem{Built a scalable platform for seamless tour booking and customer management.}
        \resumeItem{Implemented features like user authentication, search, and reviews.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/md-shafiuddin-shajib/Food-Delivery.git}{Food Delivery Website} | React.js, Redux}{2024}
      \resumeItemListStart
                \resumeItem{Designed and implemented a dynamic food delivery platform.}
        \resumeItem{Enhanced user experience with responsive design.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/md-shafiuddin-shajib/Ecommer-react.git}{E-Commerce Website} | React.js, Tailwind CSS}{2023}
      \resumeItemListStart
               \resumeItem{Built an e-commerce platform with product listings, shopping cart, and checkout.}
        \resumeItem{Provided a visually appealing and user-friendly experience.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\small{
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \textbf{Languages:} JavaScript, C, C++, Java, SQL
  \item \textbf{Technologies/Frameworks:} HTML, CSS, React, Redux, Node.js, Express.js, MongoDB, Tailwind CSS
  \item \textbf{Tools:} VS Code, Git, GitHub, Figma
  \item \textbf{Soft Skills:} Problem Solving, Team Collaboration, Communication, Time Management
\end{itemize}
}

%-----------LANGUAGES-----------
\section{Languages}
\begin{itemize}[itemsep=0pt]
    \item Proficient in English
    \item Native in Bangla
\end{itemize}

\end{document}
